\sysfull

### 2018-04-15 paper/implementation.tex

@@

\textbf{New tasks.} The API method \texttt{COALA\_TASK} statically allocates a non-volatile constant variable holding the task weight, and declares a void function with the name passed as an argument.

New protected variables. The API method \texttt{COALA\_PV} statically allocates (and aligns in memory) a non-volatile variable, whose address will be used by RP and WP to locate the most recent location of the variable itself, which could be either the location of the variable in volatile memory or its location in non-volatile memory.

Task transitions. By calling \texttt{COALA\_NEXT\_TASK}, the user tells Coala’s scheduler what task to execute next. Note that the currently executing is not interrupted, and only once it completes the next task is run.

Protected reads and writes. When RP and WP are used, Coala searches the volatile memory for the page the protected variable belongs to. If such page is not found in RAM, then a page fault occurs, and the page is fetched from the non-volatile memory. The two functions return a handle to the variable’s volatile memory location. Unlike RP, WP marks the page being written as dirty, so that it can be committed to its non-volatile location.

Initialization and origin task. The behavior of the method \texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the addition that all the preliminary kernel initializations are performed inside this function. Moreover, the origin task is scheduled only upon the first boot.

Execution. The application control is passed to Coala’s scheduler by calling \texttt{COALA\_RUN} at the end of the main function. A high-level state machine of the scheduler is depicted in Figure \textcolor{red}{[draw and ref figure]}. Depending on the coalescing algorithm, state transitions follow a different pattern.

\subsection{\sys Paging}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{figures/graffle/paging.pdf}
	\caption{Illustration of page tags \textcolor{red}{to be drawn}}
\end{figure}

>>>>

\textbf{New Tasks.} The API method \texttt{COALA\_TASK} statically allocates a non-volatile constant variable holding the task weight, and declares a void function with the name passed as an argument.

\textbf{New Protected Variables.} The API method \texttt{COALA\_PV} statically allocates (and aligns in memory) a non-volatile variable, whose address will be used by \texttt{RP} and \texttt{WP} API methods to locate the most recent location of the variable itself, which could be either the location of the variable in volatile memory or its location in a non-volatile memory.

\textbf{Task Transitions.} By calling \texttt{COALA\_NEXT\_TASK} API method, the programmer tells \sys's scheduler what task to execute next. The \sys kernel implementation is built on the assumption that the currently executing task is not interrupted, and only once it completes the next task is run. \todo{Provide information on the implementation - this paragraph repeats simply what previous section did}{Carlo}

\textbf{Protected Reads and Writes.} When \texttt{RP} and \texttt{WP} API mentods are used, \sys searches the volatile memory for the page the protected variable belongs to. If such page is not found in RAM, then a page fault occurs, and the page is fetched from the non-volatile memory. The two functions return a handle to the variable's volatile memory location. Unlike \texttt{RP}, \texttt{WP} marks the page being written as dirty, so that it can be committed to its non-volatile location.

\textbf{Initialization and Origin Task.} The behavior of the API method \texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the addition that all the preliminary kernel initializations are performed inside this function. Moreover, the origin task is scheduled only upon the first boot.

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	%\includegraphics[width=0.5\columnwidth]{figures/graffle/overview.pdf}
	\caption{\sys state machine implementation \todo{Draw a figure}{Sinan, Carlo}}
	\label{fig:coala_state_machine}
\end{wrapfigure}

\textbf{Execution.} The application control is passed to \sys's scheduler by calling \texttt{COALA\_RUN} at the end of the main function. A high-level state machine of the scheduler is depicted in Figure~\ref{fig:coala_state_machine} \todo{Draw a figure; provide more text on the execution}{Carlo}.

\subsection{\sys Paging Implementation}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{figures/graffle/paging.pdf}
	\caption{Illustration of \sys page tags.}
\end{figure}
